Hierarchical models and seq model fits

### 2025-04-04 documentation/hierarchicalmodels_seqruns.qmd
document function to get subhierarchy estimates

-   We clean up helper functions, so that they take in the mu_stars, and specific other stan_data, and are better documented. See function extract_parameter_subhierarchical_simplified in fit_model_simplified R script, and its usage below.

```{r}
fit <- fit1a
# some notes, to understand updates between this code base and original one
# and where to find info 
#fit1a$country_index is now fit$geo_unit
# see fit1a$hierarchical_level for info
# hierarchical_data(fit$geo_unit, fit$hierarchical_level)
# note that subhierarchies are called column in hierarchical data
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
    extract_parameter_subhierarchical_simplified (
      hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples)
}
# mu[[]] has posterior samples for the subhierarchy level
# to get the summaries
quantile_df <- function(x, probs = c(0.025, 0.5, 0.975)) {
  tibble(
    val = quantile(x, probs, na.rm = TRUE),
    quant = probs
  )
}
res_global <- map(mu, function(tibble_samples) 
  tibble_samples %>% select(name, value)  %>% reframe(quantile_df(value), .by = name))
res_global

@@

```{r}
fit <- fit_local
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
    extract_parameter_subhierarchical_simplified (
      hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples)
}
res_local <- map(mu, function(tibble_samples) 
  tibble_samples %>% select(name, value)  %>% reframe(quantile_df(value), .by = name))
res_local
```

@@

```{r}
prefixed_param_name
```

>>>>

-   We clean up helper functions, so that they take in the mu_stars, and specific other stan_data, and are better documented. See function extract_parameter_subhierarchical in fit_model_simplified R script, and its usage below.

```{r}
quantile_df <- function(x, probs = c(0.025, 0.5, 0.975)) {
  tibble(
    val = quantile(x, probs, na.rm = TRUE),
    quant = probs
  )
}
```

```{r}
fit <- fit1a
# some notes, to understand updates between this code base and original one
# and where to find info 
#fit1a$country_index is now fit$geo_unit
# see fit1a$hierarchical_level for info
# hierarchical_data(fit$geo_unit, fit$hierarchical_level)
# note that subhierarchies are called column in hierarchical data
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
    extract_parameter_subhierarchical (
      hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples)
}
# mu[[]] has posterior samples for the subhierarchy level
# to get the summaries

res_global <- map(mu, function(tibble_samples) 
  tibble_samples %>% select(name, value)  %>% reframe(quantile_df(value), .by = name))
res_global

@@

```{r}
fit <- fit_local
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
    extract_parameter_subhierarchical (
      hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples)
}
res_local <- map(mu, function(tibble_samples) 
  tibble_samples %>% select(name, value)  %>% reframe(quantile_df(value), .by = name))
res_local
```

@@

```{r}
#prefixed_param_name
```

### 2025-04-04 documentation/hierarchicalmodels_seqruns_2par.qmd
document function to get subhierarchy estimates

```{r}
subhierarchy <- fit$hierarchical_level[1]
hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level)
parname = "mu"
fit_samples = fit$samples

@@

```{r}
fit <- fit1a
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
    extract_parameter_subhierarchical_simplified_kparam(
      hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples)
}

@@

```{r}
fit <- fit_local
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
#    extract_parameter_subhierarchical_simplified (
  extract_parameter_subhierarchical_simplified_kparam(
    hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples)
}
res_local <- map(mu, function(tibble_samples) 
#  tibble_samples %>% select(name, value)  %>% reframe(quantile_df(value), .by = name))
    tibble_samples %>% select(name, value, k)  %>% reframe(quantile_df(value), .by = c(name, k)))
res_local
```

>>>>

```{r}
fit <- fit1a
subhierarchy <- fit$hierarchical_level[1]
hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level)
parname = "mu"
fit_samples = fit$samples

@@

```{r}
fit <- fit1a
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
    extract_parameter_subhierarchical(
      hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples,
      morethan1param = TRUE)
}

@@

```{r}
fit <- fit_local
mu <- list()
for(subhierarchy in fit$hierarchical_level) {
  mu[[subhierarchy]] <-
#    extract_parameter_subhierarchical (
  extract_parameter_subhierarchical(
    hierarchical_data = hierarchical_data(fit$geo_unit, fit$hierarchical_level),
      subhierarchy = subhierarchy,
      parname = "mu",
      fit_samples = fit$samples,
          morethan1param = TRUE)

}
res_local <- map(mu, function(tibble_samples) 
#  tibble_samples %>% select(name, value)  %>% reframe(quantile_df(value), .by = name))
    tibble_samples %>% select(name, value, k)  %>% reframe(quantile_df(value), .by = c(name, k)))
res_local
```
